---
title: "R Notebook"
output: html_notebook
---

In this fifth and final supplementary document, the results obtained from the algorithms will be compared, and some additional analyses will be provided.


```{r message=FALSE, warning=FALSE}
library(caret)
library(CustomerScoringMetrics)
Combined <- read.csv("test_comparison.csv", stringsAsFactors = F)
library(pROC)
library(dplyr)
library(tidymodels)
```

The following code chuncks show the confusion matrices, AUC and gain curves of the predictions. We start with the Lasso regression
```{r}
confusionMatrix(factor(Combined$EPS_Movement), factor(Combined$LassoPredictions))
```
```{r}
ROC <- roc(factor(Combined$EPS_Movement), Combined$LassoPredictions)
ROC$auc
```

```{r}
gain_curve(Combined, truth = factor(EPS_Movement), estimate = Lasso) %>% autoplot() 
```
Followed by the Random Forests:
```{r}
confusionMatrix(factor(Combined$EPS_Movement), factor(Combined$RFPredictions))
```

```{r}
ROC <- roc(factor(Combined$EPS_Movement), Combined$RFPredictions)
ROC$auc
```

```{r}
gain_curve(Combined, truth = factor(EPS_Movement), estimate = RF) %>% autoplot()
```

And the gradient boosting machines:
```{r}
confusionMatrix(factor(Combined$EPS_Movement), factor(Combined$GBMPredictions))
```

```{r}
ROC <- roc(factor(Combined$EPS_Movement), Combined$GBMPredictions)
ROC$auc
```

```{r}
gain_curve(Combined, truth = factor(EPS_Movement), estimate = GBM) %>% autoplot()
```

Finally, the accuracy and AUC for the IBES predictions have been calculated
```{r}
confusionMatrix(factor(Combined$EPS_Movement), factor(Combined$MoveIBES))
```

```{r}
ROC <- roc(factor(Combined$EPS_Movement), Combined$MoveIBES)
ROC$auc
```

A deeper analysis is then provided in what the differences are between sector, year and size

Observations in Industry
```{r}
Combined$Industry <- ifelse(Combined$Industry == "Agriculture, forestry and fishing" | is.na(Combined$Industry), "Other", Combined$Industry)
nrow(Combined[Combined$Industry == "Manufacturing",])
nrow(Combined[Combined$Industry == "Transportation, communication and utilities",])
nrow(Combined[Combined$Industry == "Wholesale and retail trade",])
nrow(Combined[Combined$Industry == "Services",])
nrow(Combined[Combined$Industry == "Mining",])
nrow(Combined[Combined$Industry == "Construction",])
nrow(Combined[Combined$Industry == "Other",])
```

Lasso regression + Industry
```{r}
accuracy(Combined[Combined$Industry == "Manufacturing",], factor(EPS_Movement), factor(LassoPredictions))
accuracy(Combined[Combined$Industry == "Transportation, communication and utilities",], factor(EPS_Movement), factor(LassoPredictions))
accuracy(Combined[Combined$Industry == "Wholesale and retail trade",], factor(EPS_Movement), factor(LassoPredictions))
accuracy(Combined[Combined$Industry == "Services",], factor(EPS_Movement), factor(LassoPredictions))
accuracy(Combined[Combined$Industry == "Mining",], factor(EPS_Movement), factor(LassoPredictions))
accuracy(Combined[Combined$Industry == "Construction",], factor(EPS_Movement), factor(LassoPredictions))
accuracy(Combined[Combined$Industry == "Other",], factor(EPS_Movement), factor(LassoPredictions))
```

Random Forests + Industry
```{r}

accuracy(Combined[Combined$Industry == "Manufacturing",], factor(EPS_Movement), factor(RFPredictions))
accuracy(Combined[Combined$Industry == "Transportation, communication and utilities",], factor(EPS_Movement), factor(RFPredictions))
accuracy(Combined[Combined$Industry == "Wholesale and retail trade",], factor(EPS_Movement), factor(RFPredictions))
accuracy(Combined[Combined$Industry == "Services",], factor(EPS_Movement), factor(RFPredictions))
accuracy(Combined[Combined$Industry == "Mining",], factor(EPS_Movement), factor(RFPredictions))
accuracy(Combined[Combined$Industry == "Construction",], factor(EPS_Movement), factor(RFPredictions))
accuracy(Combined[Combined$Industry == "Other",], factor(EPS_Movement), factor(RFPredictions))
```

Gradient Boosting Machines + Industry
```{r}
accuracy(Combined[Combined$Industry == "Manufacturing",], factor(EPS_Movement), factor(GBMPredictions))
accuracy(Combined[Combined$Industry == "Transportation, communication and utilities",], factor(EPS_Movement), factor(GBMPredictions))
accuracy(Combined[Combined$Industry == "Wholesale and retail trade",], factor(EPS_Movement), factor(GBMPredictions))
accuracy(Combined[Combined$Industry == "Services",], factor(EPS_Movement), factor(GBMPredictions))
accuracy(Combined[Combined$Industry == "Mining",], factor(EPS_Movement), factor(GBMPredictions))
accuracy(Combined[Combined$Industry == "Construction",], factor(EPS_Movement), factor(GBMPredictions))
accuracy(Combined[Combined$Industry == "Other",], factor(EPS_Movement), factor(GBMPredictions))
```


IBES + Industry
```{r}
## IBES industry
accuracy(Combined[Combined$Industry == "Manufacturing",], factor(EPS_Movement), factor(MoveIBES))
accuracy(Combined[Combined$Industry == "Transportation, communication and utilities",], factor(EPS_Movement), factor(MoveIBES))
accuracy(Combined[Combined$Industry == "Wholesale and retail trade",], factor(EPS_Movement), factor(MoveIBES))
accuracy(Combined[Combined$Industry == "Services",], factor(EPS_Movement), factor(MoveIBES))
accuracy(Combined[Combined$Industry == "Mining",], factor(EPS_Movement), factor(MoveIBES))
accuracy(Combined[Combined$Industry == "Construction",], factor(EPS_Movement), factor(MoveIBES))
accuracy(Combined[Combined$Industry == "Other",], factor(EPS_Movement), factor(MoveIBES))
```


Observations in Year
```{r}
nrow(Combined[Combined$Year== "2012",])
nrow(Combined[Combined$Year== "2013",])
nrow(Combined[Combined$Year == "2014",])
nrow(Combined[Combined$Year == "2015",])
nrow(Combined[Combined$Year == "2016",])
nrow(Combined[Combined$Year == "2017",])
nrow(Combined[Combined$Year == "2018",])
nrow(Combined[Combined$Year == "2019",])
```

Lasso regression + Year
```{r}
#Lasso + year
accuracy(Combined[Combined$Year == "2012",], factor(EPS_Movement), factor(LassoPredictions))
accuracy(Combined[Combined$Year == "2013",], factor(EPS_Movement), factor(LassoPredictions))
accuracy(Combined[Combined$Year == "2014",], factor(EPS_Movement), factor(LassoPredictions))
accuracy(Combined[Combined$Year == "2015",], factor(EPS_Movement), factor(LassoPredictions))
accuracy(Combined[Combined$Year == "2016",], factor(EPS_Movement), factor(LassoPredictions))
accuracy(Combined[Combined$Year == "2017",], factor(EPS_Movement), factor(LassoPredictions))
accuracy(Combined[Combined$Year == "2018",], factor(EPS_Movement), factor(LassoPredictions))
accuracy(Combined[Combined$Year == "2019",], factor(EPS_Movement), factor(LassoPredictions))
```

Random Forests + Year
```{r}
accuracy(Combined[Combined$Year == "2012",], factor(EPS_Movement), factor(RFPredictions))
accuracy(Combined[Combined$Year == "2013",], factor(EPS_Movement), factor(RFPredictions))
accuracy(Combined[Combined$Year == "2014",], factor(EPS_Movement), factor(RFPredictions))
accuracy(Combined[Combined$Year == "2015",], factor(EPS_Movement), factor(RFPredictions))
accuracy(Combined[Combined$Year == "2016",], factor(EPS_Movement), factor(RFPredictions))
accuracy(Combined[Combined$Year == "2017",], factor(EPS_Movement), factor(RFPredictions))
accuracy(Combined[Combined$Year == "2018",], factor(EPS_Movement), factor(RFPredictions))
accuracy(Combined[Combined$Year == "2019",], factor(EPS_Movement), factor(RFPredictions))
```

Gradient Bossting Machines + Year
```{r}
accuracy(Combined[Combined$Year == "2012",], factor(EPS_Movement), factor(GBMPredictions))
accuracy(Combined[Combined$Year == "2013",], factor(EPS_Movement), factor(GBMPredictions))
accuracy(Combined[Combined$Year == "2014",], factor(EPS_Movement), factor(GBMPredictions))
accuracy(Combined[Combined$Year == "2015",], factor(EPS_Movement), factor(GBMPredictions))
accuracy(Combined[Combined$Year == "2016",], factor(EPS_Movement), factor(GBMPredictions))
accuracy(Combined[Combined$Year == "2017",], factor(EPS_Movement), factor(GBMPredictions))
accuracy(Combined[Combined$Year == "2018",], factor(EPS_Movement), factor(GBMPredictions))
accuracy(Combined[Combined$Year == "2019",], factor(EPS_Movement), factor(GBMPredictions))
```

IBES + Year
```{r}
accuracy(Combined[Combined$Year == "2012",], factor(EPS_Movement), factor(MoveIBES))
accuracy(Combined[Combined$Year == "2013",], factor(EPS_Movement), factor(MoveIBES))
accuracy(Combined[Combined$Year == "2014",], factor(EPS_Movement), factor(MoveIBES))
accuracy(Combined[Combined$Year == "2015",], factor(EPS_Movement), factor(MoveIBES))
accuracy(Combined[Combined$Year == "2016",], factor(EPS_Movement), factor(MoveIBES))
accuracy(Combined[Combined$Year == "2017",], factor(EPS_Movement), factor(MoveIBES))
accuracy(Combined[Combined$Year == "2018",], factor(EPS_Movement), factor(MoveIBES))
accuracy(Combined[Combined$Year == "2019",], factor(EPS_Movement), factor(MoveIBES))
```

Observations Size
```{r}
nrow(Combined[Combined$Size== "<10M",])
nrow(Combined[Combined$Size== "10M-50M",])
nrow(Combined[Combined$Size == "50M-200M",])
nrow(Combined[Combined$Size == "200M-500M",])
nrow(Combined[Combined$Size == "500M-1B",])
nrow(Combined[Combined$Size == "1B-2B",])
nrow(Combined[Combined$Size == "2B-5B",])
nrow(Combined[Combined$Size == "5B-10B",])
nrow(Combined[Combined$Size == ">10B",])
```

Lasso regression + Size
```{r}
accuracy(Combined[Combined$Size == "<10M",], factor(EPS_Movement), factor(LassoPredictions))
accuracy(Combined[Combined$Size == "10M-50M",], factor(EPS_Movement), factor(LassoPredictions))
accuracy(Combined[Combined$Size == "50M-200M",], factor(EPS_Movement), factor(LassoPredictions))
accuracy(Combined[Combined$Size == "200M-500M",], factor(EPS_Movement), factor(LassoPredictions))
accuracy(Combined[Combined$Size == "500M-1B",], factor(EPS_Movement), factor(LassoPredictions))
accuracy(Combined[Combined$Size == "1B-2B",], factor(EPS_Movement), factor(LassoPredictions))
accuracy(Combined[Combined$Size == "2B-5B",], factor(EPS_Movement), factor(LassoPredictions))
accuracy(Combined[Combined$Size == "5B-10B",], factor(EPS_Movement), factor(LassoPredictions))
accuracy(Combined[Combined$Size == ">10B",], factor(EPS_Movement), factor(LassoPredictions))
```

Random Forests + Size
```{r}
accuracy(Combined[Combined$Size == "<10M",], factor(EPS_Movement), factor(RFPredictions))
accuracy(Combined[Combined$Size == "10M-50M",], factor(EPS_Movement), factor(RFPredictions))
accuracy(Combined[Combined$Size == "50M-200M",], factor(EPS_Movement), factor(RFPredictions))
accuracy(Combined[Combined$Size == "200M-500M",], factor(EPS_Movement), factor(RFPredictions))
accuracy(Combined[Combined$Size == "500M-1B",], factor(EPS_Movement), factor(RFPredictions))
accuracy(Combined[Combined$Size == "1B-2B",], factor(EPS_Movement), factor(RFPredictions))
accuracy(Combined[Combined$Size == "2B-5B",], factor(EPS_Movement), factor(RFPredictions))
accuracy(Combined[Combined$Size == "5B-10B",], factor(EPS_Movement), factor(RFPredictions))
accuracy(Combined[Combined$Size == ">10B",], factor(EPS_Movement), factor(RFPredictions))
```

Gradient Boosting Machines + Size
```{r}
accuracy(Combined[Combined$Size == "<10M",], factor(EPS_Movement), factor(GBMPredictions))
accuracy(Combined[Combined$Size == "10M-50M",], factor(EPS_Movement), factor(GBMPredictions))
accuracy(Combined[Combined$Size == "50M-200M",], factor(EPS_Movement), factor(GBMPredictions))
accuracy(Combined[Combined$Size == "200M-500M",], factor(EPS_Movement), factor(GBMPredictions))
accuracy(Combined[Combined$Size == "500M-1B",], factor(EPS_Movement), factor(GBMPredictions))
accuracy(Combined[Combined$Size == "1B-2B",], factor(EPS_Movement), factor(GBMPredictions))
accuracy(Combined[Combined$Size == "2B-5B",], factor(EPS_Movement), factor(GBMPredictions))
accuracy(Combined[Combined$Size == "5B-10B",], factor(EPS_Movement), factor(GBMPredictions))
accuracy(Combined[Combined$Size == ">10B",], factor(EPS_Movement), factor(GBMPredictions))
```

IBES + Size
```{r}
accuracy(Combined[Combined$Size == "<10M",], factor(EPS_Movement), factor(MoveIBES))
accuracy(Combined[Combined$Size == "10M-50M",], factor(EPS_Movement), factor(MoveIBES))
accuracy(Combined[Combined$Size == "50M-200M",], factor(EPS_Movement), factor(MoveIBES))
accuracy(Combined[Combined$Size == "200M-500M",], factor(EPS_Movement), factor(MoveIBES))
accuracy(Combined[Combined$Size == "500M-1B",], factor(EPS_Movement), factor(MoveIBES))
accuracy(Combined[Combined$Size == "1B-2B",], factor(EPS_Movement), factor(MoveIBES))
accuracy(Combined[Combined$Size == "2B-5B",], factor(EPS_Movement), factor(MoveIBES))
accuracy(Combined[Combined$Size == "5B-10B",], factor(EPS_Movement), factor(MoveIBES))
accuracy(Combined[Combined$Size == ">10B",], factor(EPS_Movement), factor(MoveIBES))
```
